Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-05-28 LaTeX_paper/paper.tex
fix margins

@@

\section{Abstract}
The jigsaw puzzle problem has been in the eye of computer scientists for a while,
and some clever solutions have already been found. These algorithms are made to
work with a “digital” jigsaw puzzle [\ref{fig:figure_digital_puzzle}],
there aren't papers (at least not popular enough to be searchable)
that try to apply the solution
to a “real world” jigsaw puzzle [\ref{fig:figure_real_puzzle}].\newline
The problem has been tackled by some small projects. But, as said earlier,
the process and eventual challenges has never been documented by a paper,
this wants to be the first.\newline
As a Bonus the paper will also cover the creation of a user friendly app
that will be open source and free to use.

>>>>

\usepackage[a4paper, total={6.5in, 9in}]{geometry}

@@

\section{Abstract}
The jigsaw puzzle problem has been in the eye of computer scientists for a while,
and some clever solutions have already been found. These algorithms are made to
work with a “digital” jigsaw puzzle [\ref{fig:figure_digital_puzzle}],
but there aren't papers (at least not popular enough to be searchable)
that try to apply the solution
to a “real world” jigsaw puzzle [\ref{fig:figure_real_puzzle}].\newline
The problem has been tackled by some small projects. But, as said earlier,
the process and eventual challenges has never been documented by a paper,
this wants to be the first.\newline
As a bonus the paper will also cover the creation of a user friendly app
that will be open source and free to use.
